Quantifying the importance of an inference model in Bayesian phylogenetics

### 2020-06-26 pirouette_article.tex
Process feedback @rsetienne

The goal of \verb;pirouette; is to quantify the \new{impact of a new} tree prior.
It does so by measuring the inference error made 
for a given reconstructed phylogeny, 
simulated under a (usually novel) diversification model.
We refer to the model that has generated the given tree 
as the 'generative tree model' $\mathit{p_{G}}$.
\rampal{This only increases the confusion; maybe replace by baseline model everywhere}
\new{
  A 'generative tree model', in this paper, is always a standard tree model.
  If the actual model that generated the tree is non-standard, 
  the 'generative tree model' is the (standard) tree model that is (assumed
  to be) closest to the actual (non-standard) model. In that case, the
  'generative tree model' can also be called 'baseline model' 
  or 'comparison model'.
}

>>>>

The goal of \verb;pirouette; is to quantify the \new{impact of a new} tree prior.
It does so by measuring the inference error made 
for a given reconstructed phylogeny, 
simulated under a (usually novel) diversification model.
We refer to the model that has generated the given tree 
as the 'generative tree model' $\mathit{p_{G}}$.
\rampal{
	This only increases the confusion; maybe replace by baseline model everywhere
}
\richel{
	I feel the new wording below is good enough. Replacing 'generative'
	by 'baseline' add to confustion when the generative model is the
	generative model. Giovanni, what do you think?
}
\new{
  A 'generative tree model', in this paper, is always a standard tree model.
  If the actual model that generated the tree is non-standard, 
  the 'generative tree model' is the standard tree model that is 
  closest to the actual model. In that case, the
  'generative tree model' serves as a baseline or comparison model.
}
